---
title: "AnneArundel"
author: "Nicole Williamson"
date: "2023-01-23"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE, message=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE, message=FALSE, warning=FALSE}
#Install/load packages
library("tidyr")
library("dplyr")
library("readr")
library("ggplot2")
library("scales")
library("ggpubr")
```

```{r, include=FALSE, message=FALSE, warning=FALSE}
# Code for joining data sets (could use left or right join instead) 
MyMerge       <- function(x, y){
  df            <- merge(x, y, all = TRUE)
  rownames(df)  <- df$Row.names
  df$Row.names  <- NULL
  return(df)
}
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# read in water usage data
waterusage <- read.csv("../Data/WaterUsage_AnneArundelCounty_2022.csv") %>% select(permit, year, annual_avg)

#str(waterusage)
#unique(waterusage$permit)
```

# **All Permits, 2000-2022** 
   Still need to figure out a better way to distinguish the colors
```{r, echo=FALSE, message=FALSE, warning=FALSE}

waterusage_2000 <- waterusage %>% filter(year > 1999) 
ggplot(data = waterusage_2000, aes(x = year, y= annual_avg, color = permit))+
  scale_color_manual(values = c("AA1953G008" = "#f44336",
                                "AA1953G108" = "#e81e63",
                                "AA1953G208" = "#9c27b0",
                                "AA1968G006" = "#673ab7",
                                "AA1969G019" = "#3f51b5",
                                "AA1972G005" = "#2196f3",
                                "AA1972G105" = "#03a9f4",
                                "AA1981G025" = "#00bcd4",
                                "AA1981G026" = "#009688",
                                "AA1982G036" = "#4caf50",
                                "AA1982G037" = "#8bc34a",
                                "AA1982G039" = "#cddc39",
                                "AA1982G044" = "#ffeb3b",
                                "AA1986G070" = "#ffc107",
                                "AA1987G069" = "#ff9800",
                                "AA2005G020" = "#ff5722"))+
  geom_line(size = 1)+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
  scale_y_continuous(labels = label_comma())+
  scale_x_continuous(limits = c(2000, 2022), breaks = seq(2000, 2022, 1))+
 # geom_hline(yintercept = 41000000, color = "black", linetype= "dashed")+
#  annotate("text", x = 2000, y= 48000000, label = "System cap - 41 million gpd")+
  labs(y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

ggsave("../Figures/AnneArundelCounty_WaterUsage.jpeg")
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
# get total avg usage across all permits for each year 
total_avg_usage <- waterusage %>% group_by(year) %>% summarise_at(vars(annual_avg), list(annual_avg = sum ), na.rm = TRUE)
total_avg_usage["permit"] <- c("total_annual_avg")

# Join the two datasets 
waterusage_total <- Reduce(MyMerge, list(waterusage, total_avg_usage))



#check for errors in naming convention 
#unique(waterusage$permit)

#max(waterusage$annual_avg)
```

# **All Permits, 1979-2022 - with annual use total** 
   Total water usage (solid black line) compared to system cap (dotted black line). The gray line is the linear projection of water use growth over time, based on **all previous years data.** Water use would exceed cap in 2032.
```{r, echo=FALSE, message=FALSE, warning=FALSE}

ggplot(data = waterusage_total, aes(x = year, y= annual_avg, color = permit))+
  scale_color_manual(values = c("AA1953G008" = "#f44336",
                                "AA1953G108" = "#e81e63",
                                "AA1953G208" = "#9c27b0",
                                "AA1968G006" = "#673ab7",
                                "AA1969G019" = "#3f51b5",
                                "AA1972G005" = "#2196f3",
                                "AA1972G105" = "#03a9f4",
                                "AA1981G025" = "#00bcd4",
                                "AA1981G026" = "#009688",
                                "AA1982G036" = "#4caf50",
                                "AA1982G037" = "#8bc34a",
                                "AA1982G039" = "#cddc39",
                                "AA1982G044" = "#ffeb3b",
                                "AA1986G070" = "#ffc107",
                                "AA1987G069" = "#ff9800",
                                "AA2005G020" = "#ff5722", 
                                "total_annual_avg" = "black"))+
  geom_line(size = .75)+
  geom_smooth(data= waterusage_total %>% filter(permit == "total_annual_avg"), method = "lm", se = FALSE, fullrange = TRUE, linetype = "solid", aes(color = "gray"))+
  stat_regline_equation(label.x= 1980, label.y= 39000000, color = "black", size = 3)+ #adds regression line
  #stat_cor(aes(label=..rr.label..), label.x=0.4, label.y=.25, color = "black", size = 3)+ #adds R2 
  #stat_cor(method = "pearson", label.x = 1988, label.y = 39000000, color = "black", size = 3)+ #adds p-value 
  #xlim(1980, 2035)+
   scale_x_continuous(limits = c(1979, 2035), breaks = seq(1979, 2035, 2))+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
  scale_y_continuous(labels = label_comma())+
  geom_hline(yintercept = 41000000, color = "black", linetype= "dashed")+
  annotate("text", x = 2000, y= 43000000, label = "System cap - 41 million gpd")+
  labs(y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

#ggsave("../Figures/AnneArundelCounty_WaterUsage_SystemCap.jpeg")
```

# **All Permits, 1996-2022 - with annual use total** 
   Total water usage (solid black line) compared to system cap (dotted black line). The gray line is the linear projection of water use growth over time, based on data from the last two permit periods **from 1996 - 2022.** Water use would exceed cap in 2032.
```{r, echo=FALSE, message=FALSE, warning=FALSE}

waterusage_total_1996 <- waterusage_total %>% filter(year > 1995)

ggplot(data = waterusage_total_1996, aes(x = year, y= annual_avg, color = permit))+
  scale_color_manual(values = c("AA1953G008" = "#f44336",
                                "AA1953G108" = "#e81e63",
                                "AA1953G208" = "#9c27b0",
                                "AA1968G006" = "#673ab7",
                                "AA1969G019" = "#3f51b5",
                                "AA1972G005" = "#2196f3",
                                "AA1972G105" = "#03a9f4",
                                "AA1981G025" = "#00bcd4",
                                "AA1981G026" = "#009688",
                                "AA1982G036" = "#4caf50",
                                "AA1982G037" = "#8bc34a",
                                "AA1982G039" = "#cddc39",
                                "AA1982G044" = "#ffeb3b",
                                "AA1986G070" = "#ffc107",
                                "AA1987G069" = "#ff9800",
                                "AA2005G020" = "#ff5722", 
                                "total_annual_avg" = "black"))+
  geom_line(size = .75)+
  geom_smooth(data=waterusage_total_1996 %>% filter(permit == "total_annual_avg"), method = "lm", se = FALSE, fullrange = TRUE, linetype = "solid", aes(color = "gray"))+
  stat_regline_equation(label.x= 1996, label.y= 39000000, color = "black", size = 3)+ #adds regression line
  #stat_cor(aes(label=..rr.label..), label.x=0.4, label.y=.25, color = "black", size = 3)+ #adds R2 
  #stat_cor(method = "pearson", label.x = 1988, label.y = 39000000, color = "black", size = 3)+ #adds p-value 
  #xlim(1980, 2035)+
   scale_x_continuous(limits = c(1996, 2035), breaks = seq(1996, 2035, 2))+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
  scale_y_continuous(labels = label_comma())+
  geom_hline(yintercept = 41000000, color = "black", linetype= "dashed")+
  annotate("text", x = 2012, y= 43000000, label = "System cap - 41 million gpd")+
  labs(y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

#ggsave("../Figures/AnneArundelCounty_WaterUsage_SystemCap.jpeg")
```

# **All Permits, 2010-2022 - with annual use total** 
   Total water usage (solid black line) compared to system cap (dotted black line). The gray line is the linear projection of water use growth over time, based on data from the last permit periods **from 2010 - 2022.** Water use would exceed cap in 2029.
```{r, echo=FALSE, message=FALSE, warning=FALSE}

waterusage_total_2010 <- waterusage_total %>% filter(year > 2009)

ggplot(data = waterusage_total_2010, aes(x = year, y= annual_avg, color = permit))+
  scale_color_manual(values = c("AA1953G008" = "#f44336",
                                "AA1953G108" = "#e81e63",
                                "AA1953G208" = "#9c27b0",
                                "AA1968G006" = "#673ab7",
                                "AA1969G019" = "#3f51b5",
                                "AA1972G005" = "#2196f3",
                                "AA1972G105" = "#03a9f4",
                                "AA1981G025" = "#00bcd4",
                                "AA1981G026" = "#009688",
                                "AA1982G036" = "#4caf50",
                                "AA1982G037" = "#8bc34a",
                                "AA1982G039" = "#cddc39",
                                "AA1982G044" = "#ffeb3b",
                                "AA1986G070" = "#ffc107",
                                "AA1987G069" = "#ff9800",
                                "AA2005G020" = "#ff5722", 
                                "total_annual_avg" = "black"))+
  geom_line(size = .75)+
  geom_smooth(data=waterusage_total_2010 %>% filter(permit == "total_annual_avg"), method = "lm", se = FALSE, fullrange = TRUE, linetype = "solid", aes(color = "gray"))+
  stat_regline_equation(label.x= 2010, label.y= 39000000, color = "black", size = 3)+ #adds regression line
  #stat_cor(aes(label=..rr.label..), label.x=0.4, label.y=.25, color = "black", size = 3)+ #adds R2 
  #stat_cor(method = "pearson", label.x = 1988, label.y = 39000000, color = "black", size = 3)+ #adds p-value 
  #xlim(1980, 2035)+
   scale_x_continuous(limits = c(2010, 2035), breaks = seq(2010, 2035, 2))+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
  scale_y_continuous(labels = label_comma())+
  geom_hline(yintercept = 41000000, color = "black", linetype= "dashed")+
  annotate("text", x = 2020, y= 43000000, label = "System cap - 41 million gpd")+
  labs(y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

#ggsave("../Figures/AnneArundelCounty_WaterUsage_SystemCap.jpeg")
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
### Transform data from long to wide
wide_water <- waterusage %>% pivot_wider(names_from = "permit", values_from = annual_avg)
```

# **Individual Permit Water Usage** 

## AA1953G008
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = wide_water, aes(x = year, y= AA1953G008))+
  geom_line(size = .75, color = "#f44336")+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
scale_y_continuous(labels = label_comma())+
  scale_x_continuous(breaks = seq(1979, 2022, 2))+
 geom_hline(yintercept = 7000000, color = "#f44336", linetype= "dashed")+
  annotate("text", x = 1988, y= 7200000, label = "Permitted annual average - 7,000,000 gpd", color = "#f44336")+
  labs(title = "AA1953G008 - Water Usage", y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

ggsave("../Figures/AA1953G008_WaterUsage.jpeg")
```

## AA1953G108
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = wide_water, aes(x = year, y= AA1953G108))+
  geom_line(size = .75, color = "#e81e63")+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
 scale_y_continuous(labels = label_comma())+
  scale_x_continuous(breaks = seq(1979, 2022, 2))+
 geom_hline(yintercept = 450000, color = "#e81e63", linetype= "dashed")+
  annotate("text", x = 1988, y= 470000, label = "Permitted annual average - 450,000 gpd", color = "#e81e63")+
  labs(title = "AA1953G108 - Water Usage", y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

ggsave("../Figures/AA1953G108_WaterUsage.jpeg")
```

## AA1953G208
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = wide_water, aes(x = year, y= AA1953G208))+
  geom_line(size = .75, color = "#9c27b0")+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
 scale_y_continuous(labels = label_comma())+
  scale_x_continuous(breaks = seq(1979, 2022, 2))+
 geom_hline(yintercept = 1600000, color = "#9c27b0", linetype= "dashed")+
  annotate("text", x = 1988, y= 1650000, label = "Permitted annual average - 1,600,000 gpd", color = "#9c27b0")+
  labs(title = "AA1953G208 - Water Usage", y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

ggsave("../Figures/AA1953G208_WaterUsage.jpeg")
```

## AA1968G006
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = wide_water, aes(x = year, y= AA1968G006))+
  geom_line(size = .75, color = "#673ab7")+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
  scale_y_continuous(labels = label_comma())+
  scale_x_continuous(breaks = seq(1979, 2022, 2))+
 geom_hline(yintercept = 1400000, color = "#673ab7", linetype= "dashed")+
  annotate("text", x = 1984, y= 1450000, label = "Permitted annual average", color = "#673ab7")+
  annotate("text", x = 1984, y= 1350000, label = "1,400,000 gpd", color = "#673ab7")+
  labs(title = "AA1968G006 - Water Usage", y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

ggsave("../Figures/AA1968G006_WaterUsage.jpeg")
```

## AA1969G019
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = wide_water, aes(x = year, y= AA1969G019))+
  geom_line(size = .75, color = "#3f51b5")+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
  scale_y_continuous(labels = label_comma())+
  scale_x_continuous(breaks = seq(1979, 2022, 2))+
 geom_hline(yintercept = 4800000, color = "#3f51b5", linetype= "dashed")+
  annotate("text", x = 2000, y= 5200000, label = "Permitted annual average - 4,800,000 gpd", color = "#3f51b5")+
  labs(title = "AA1969G019 - Water Usage", y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

ggsave("../Figures/AA1969G019_WaterUsage.jpeg")
```

## AA1972G005
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = wide_water, aes(x = year, y= AA1972G005))+
  geom_line(size = .75, color = "#2196f3")+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
  scale_y_continuous(labels = label_comma())+
  scale_x_continuous(breaks = seq(1979, 2022, 2))+
 geom_hline(yintercept = 8000000, color = "#2196f3", linetype= "dashed")+
  annotate("text", x = 1988, y= 8200000, label = "Permitted annual average - 8,000,000 gpd", color = "#2196f3")+
  labs(title = "AA1972G005 - Water Usage", y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

ggsave("../Figures/AA1972G005_WaterUsage.jpeg")
```

## AA1972G105
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = wide_water, aes(x = year, y= AA1972G105))+
  geom_line(size = .75, color = "#03a9f4")+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
  scale_y_continuous(labels = label_comma())+
  scale_x_continuous(breaks = seq(1979, 2022, 2))+
 geom_hline(yintercept = 6800000, color = "#03a9f4", linetype= "dashed")+
  annotate("text", x = 1988, y= 7000000, label = "Permitted annual average - 6,800,000 gpd", color = "#03a9f4")+
  labs(title = "AA1972G105 - Water Usage", y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

ggsave("../Figures/AA1972G105_WaterUsage.jpeg")
```

## AA1981G025
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = wide_water, aes(x = year, y= AA1981G025))+
  geom_line(size = .75, color = "#00bcd4")+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
  scale_y_continuous(labels = label_comma())+
  scale_x_continuous(breaks = seq(1979, 2022, 2))+
 geom_hline(yintercept = 830000, color = "#00bcd4", linetype= "dashed")+
  annotate("text", x = 1988, y= 850000, label = "Permitted annual average - 830,000 gpd", color = "#00bcd4")+
  labs(title = "AA1981G025 - Water Usage", y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

ggsave("../Figures/AA1981G025_WaterUsage.jpeg")
```

## AA1981G026
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = wide_water, aes(x = year, y= AA1981G026))+
  geom_line(size = .75, color = "#009688")+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
  scale_y_continuous(labels = label_comma())+
  scale_x_continuous(breaks = seq(1979, 2022, 2))+
 geom_hline(yintercept = 1000000, color = "#009688", linetype= "dashed")+
  annotate("text", x = 1988, y= 1030000, label = "Permitted annual average - 1,000,000 gpd", color = "#009688")+
  labs(title = "AA1981G026 - Water Usage", y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

ggsave("../Figures/AA1981G026_WaterUsage.jpeg")
```

## AA1982G036
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = wide_water, aes(x = year, y= AA1982G036))+
  geom_line(size = .75, color = "#4caf50")+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
  scale_y_continuous(labels = label_comma())+
  scale_x_continuous(breaks = seq(1979, 2022, 2))+
 geom_hline(yintercept = 3500000, color = "#4caf50", linetype= "dashed")+
   annotate("text", x = 1988, y= 3600000, label = "Permitted annual average - 3,500,000 gpd", color = "#4caf50")+
  labs(title = "AA1982G036 - Water Usage", y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

ggsave("../Figures/AA1982G036_WaterUsage.jpeg")
```

## AA1982G037
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = wide_water, aes(x = year, y= AA1982G037))+
  geom_line(size = .75, color = "#8bc34a")+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
  scale_y_continuous(labels = label_comma())+
  scale_x_continuous(breaks = seq(1979, 2022, 2))+
 geom_hline(yintercept = 2200000, color = "#8bc34a", linetype= "dashed")+
  annotate("text", x = 1988, y= 2280000, label = "Permitted annual average - 2,200,000 gpd", color = "#8bc34a")+
  labs(title = "AA1982G037 - Water Usage", y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

ggsave("../Figures/AA1982G037_WaterUsage.jpeg")
```

## AA1982G039
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = wide_water, aes(x = year, y= AA1982G039))+
  geom_line(size = .75, color = "#cddc39")+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
  scale_y_continuous(labels = label_comma())+
  scale_x_continuous(breaks = seq(1979, 2022, 2))+
 geom_hline(yintercept = 860000, color = "#cddc39", linetype= "dashed")+
  annotate("text", x = 1988, y= 885000, label = "Permitted annual average - 860,000 gpd", color = "#cddc39")+
  labs(title = "AA1982G039 - Water Usage", y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

ggsave("../Figures/AA1982G039_WaterUsage.jpeg")
```

## AA1982G044
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = wide_water, aes(x = year, y= AA1982G044))+
  geom_line(size = 1, color = "#ffeb3b")+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
  scale_y_continuous(labels = label_comma())+
  scale_x_continuous(breaks = seq(1979, 2022, 2))+
 geom_hline(yintercept = 900000, color = "#ffeb3b", linetype= "dashed", size = 1)+
  annotate("text", x = 1988, y= 925000, label = "Permitted annual average - 900,000 gpd", color = "light grey")+
  labs(title = "AA1982G044 - Water Usage", y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

ggsave("../Figures/AA1982G044_WaterUsage.jpeg")
```

## AA1986G070
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = wide_water, aes(x = year, y= AA1986G070))+
  geom_line(size = .75, color = "#ffc107")+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
  scale_y_continuous(labels = label_comma())+
  scale_x_continuous(breaks = seq(1979, 2022, 2))+
 geom_hline(yintercept = 3600000, color = "#ffc107", linetype= "dashed")+
  annotate("text", x = 1988, y= 3700000, label = "Permitted annual average - 3,600,000 gpd", color = "#ffc107")+
  labs(title = "AA1986G070 - Water Usage", y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

ggsave("../Figures/AA1986G070_WaterUsage.jpeg")
```

## AA1987G069
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = wide_water, aes(x = year, y= AA1987G069))+
  geom_line(size = .75, color = "#ff9800")+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
  scale_y_continuous(labels = label_comma())+
  scale_x_continuous(breaks = seq(1979, 2022, 2))+
 geom_hline(yintercept = 8000000, color = "#ff9800", linetype= "dashed")+
  annotate("text", x = 1988, y= 8250000, label = "Permitted annual average - 8,000,000 gpd", color = "#ff9800")+
  labs(title = "AA1987G069 - Water Usage", y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

ggsave("../Figures/AA1987G069_WaterUsage.jpeg")
```

## AA2005G020
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = wide_water, aes(x = year, y= AA2005G020))+
  geom_line(size = .75, color = "#ff5722")+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
  scale_y_continuous(labels = label_comma())+
  scale_x_continuous(breaks = seq(1979, 2022, 2))+
 geom_hline(yintercept = 4500000, color = "#ff5722", linetype= "dashed")+
  annotate("text", x = 1988, y= 4600000, label = "Permitted annual average - 4,500,000 gpd", color = "#ff5722")+
  labs(title = "AA2005G020 - Water Usage", y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

ggsave("../Figures/AA2005G020_WaterUsage.jpeg")
```

# Supplemental permit conditions
## AA1953G008 + AA1953G108 + AA1953G208
```{r, echo=FALSE, message=FALSE, warning=FALSE}
AA1953G008_sup <- wide_water %>% select(AA1953G008, AA1953G108, AA1953G208, year) %>% pivot_longer(!year, names_to = "permit", values_to = "annual_avg")

# get total avg usage across the permits for each year 
total_AA1953G008_sup <- AA1953G008_sup %>% group_by(year) %>% summarise_at(vars(annual_avg), list(annual_avg = sum ), na.rm = TRUE)
total_AA1953G008_sup["permit"] <- c("total_annual_avg")

# Join the two datasets 
AA1953G008_sup <- Reduce(MyMerge, list(AA1953G008_sup, total_AA1953G008_sup))

#Specify drawing order
AA1953G008_sup$permit <- factor(AA1953G008_sup$permit, levels = c("AA1953G008", "AA1953G108", "AA1953G208", "total_annual_avg"))

ggplot(data = AA1953G008_sup, aes(x = year, y= annual_avg, color = permit))+
  scale_color_manual(values = c("AA1953G008" = "#f44336",
                                "AA1953G108" = "#e81e63",
                                "AA1953G208" = "#9c27b0",
                                "total_annual_avg" = "black"))+
  geom_line(data = subset(AA1953G008_sup, permit == "total_annual_avg"), size = .75)+
  geom_line(data = subset(AA1953G008_sup, permit == "AA1953G208"), size = .75)+
geom_line(data = subset(AA1953G008_sup, permit == "AA1953G108"), size = .75)+
  geom_line(data = subset(AA1953G008_sup, permit == "AA1953G008"), size = .75)+
  theme_light()+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(color = "black", size = 8),
        axis.line = element_line(colour = "black", linetype = "solid"), 
        legend.position="none",
        plot.title = element_text(hjust = .5))+
  scale_y_continuous(labels = label_comma())+
  scale_x_continuous(breaks = seq(1979, 2022, 2))+
  geom_hline(yintercept = 9050000, color = "black", linetype= "dashed")+
  annotate("text", x = 2000, y= 9400000, label = "System cap - 9.05 million gpd")+
  labs(title = "Supplemental permit conditions - AA1953G008/AA1953G108/AA1953G208", y = "Annual Average Water Ussage (gpd)", x = "Year")+
  guides(color=guide_legend(" "))+
  theme(legend.position="bottom")

ggsave("../Figures/AA1953G008_sup_WaterUsage.jpeg")
```


